\section{Definitions}
Throughout the specification a following list of terms is widely used. In this section we define their meaning 
and what assumptions do we make on them.

\medskip
\textbf{Email}: Email client that allows the user to gain read access rights to the inbox associated
with the email address he/she provided. It is assumed that the user is the only person with the read access 
to this entity.

\medskip
\textbf{Auth}: Central authentication provider that serves as a secure token store (STS) and conforms to 
the Raccu Auth Provider API Specification. Valid and trusted certificate issued from the certificate authority (CA)
as a part of public key infrastructure (PKI) for this entity is implied.

\medskip
\textbf{Mobile}: A mobile application implementation conforming to the Raccu Mobile Application Specification 
that communicates with the corresponding Auth instance. Access to the fingerprint reader and an enabled biometric 
authentication on the host smartphone is implied.

\medskip
\textbf{Browser}: A client-side component in charge of rendering QR codes and dispatching appropriate messages 
as specified by this specification and a separate Raccu Client Component Specification. 

\medskip
\textbf{Attestation}: Digitally signed claim in a form of a token that confirms holder's identity. Issued by 
an Auth instance in a format defined in this specification and a separate Raccu Auth Provider API Specification. 
A secure storing of the attestation by its holder is implied.

\medskip
\textbf{Server}: An end web service or application that consumes an attestation issued by an Auth instance. 
Authorization service within the Server is assumed. Valid and trusted certificate issued as a part of PKI 
for this entity is implied.

\medskip
The key words "MUST", "MUST NOT", "REQUIRED", "SHALL", "SHALL NOT", "SHOULD", "SHOULD NOT", "RECOMMENDED", 
"MAY", and "OPTIONAL" in this specification are to be interpreted as described in 
\href{https://tools.ietf.org/html/rfc2119}{RFC 2119} and \href{https://tools.ietf.org/html/rfc8174}{RFC 8174}.