\section{Introduction}
This specification provides a formal, high-level overview of the Raccu protocol. 

    \subsection{Background}
    Raccu is a centralized \ac{sts} protocol for public-key cryptography authentication based on a 
    smartphone biometry. The protocol is architecturally inspired by the likes of OAuth 2.0, OpenID, 
    and W3C's WebAuthn while it conceptually resembles FIDO Alliance's \ac{ctap}, namely FIDO UAF standards. 

    \subsection{Goals}
    The core vision of Raccu is to provide a uniform method of authentication with the following properties: 
        \begin{enumerate}
            \item Smaller complexity and lesser cognitive load than in a traditional email and password 
                  authentication systems.
            \item Single registration process for authenticating to multiple web services and applications.
            \item Authentication process for issuing an attestation is independent of the type of registration 
                  used to create an account.
            \item Preserving data and origin integrity of the attestation through PKI based chain of trust.
            \item Requiring user's consent via independent biometric authorization process before granting an 
                  attestation.
        \end{enumerate}
    In the current version of the protocol, only an email-based registration is described in details, although 
    other types of registrations and verification claims can be easily added if needed.

    \subsection{Disclaimer}
    Implementation of certain elements of this specification may require licenses under third party intellectual 
    property rights, including without limitation, patent rights. The authors and any other contributors to this 
    specification are not, and shall not be held, responsible in any manner for identifying or failing to identify 
    any or all such third party intellectual property rights.    
    
    \medskip
    THIS SPECIFICATION IS PROVIDED “AS IS” AND WITHOUT ANY WARRANTY OF ANY KIND, INCLUDING, WITHOUT LIMITATION,
    ANY EXPRESS OR IMPLIED WARRANTY OF NON-INFRINGEMENT, MERCHANTABILITY OR FITNESS FOR A PARTICULAR PURPOSE.

    \subsection{Contributing}
    Anyone can contribute to the protocol or to its specification. To learn more about contributing, please visit our 
    official repository on GitHub located at \href{https://www.github.com/Raccu/Documentation}{https://www.github.com/Raccu/Documentation}.